Wigglyhedra

### 2024-11-07 FPSAC25/wigglyhedraFPSAC.tex
minor corrections

In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, $\delta_0 \eqdef \delta_{n+1} \eqdef 0$.
We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice % of \cref{sec:wigglyPermutations} 
and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron. % of \cref{sec:wigglyhedron}.
\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in \cref{fig:wigglyCambrian}.

>>>>

In this section, we fix a signature~$\delta \eqdef \delta_1 \dots \delta_n \in \{+,-\}^n$. By convention, $\delta_0 \eqdef \delta_{n+1} \eqdef 0$.
We connect the $\delta$-Cambrian lattice~\cite{Reading-CambrianLattices} to the wiggly lattice % of \cref{sec:wigglyPermutations} 
and the $\delta$-associahedron of~\cite{HohlwegLange} to the wigglyhedron. % of \cref{sec:wigglyhedron}.
\cref{def:CambrianTriangulations,def:CambrianPermutations,def:CambrianWigglyPseudotriangulations,def:CambrianWigglyPermutations,prop:CambrianLattice} are illustrated in~\cref{fig:wigglyCambrian}.
